\section{Market-Making Logic on Exchange A}
\label{sec:quoter}

Exchange $A$ has no history, so every quote we post is derived
from the state of $B$, $C$, our inventory $q$, and our capital $K$.
Given these inputs the quoter must output two things each step: the
set of orders to post and the set of resting orders to cancel. We
describe here the modelling decisions that produce those two lists,
not the Python that assembles them. The six subsections follow the
order in which the decisions are composed: read the reference price,
compute a reservation price, widen a spread around it, skew
asymmetrically and lay down a ladder, decide whether to re-quote at
all, and finally hedge when inventory breaches its limit.

\subsection{Fair mid under latency asymmetry}
\label{sec:quoter-mid}

We never quote against $A$'s own mid: $A$ has no informative price
until we seed one. The reference is instead a cross-venue best
constructed from $B$ and $C$ read with their respective latency
offsets $\ell_B = 200\,\mathrm{ms}$ and $\ell_C = 170\,\mathrm{ms}$,
\[
  \mathrm{bid}^{\mathrm{fair}}_t = \max\!\bigl(\mathrm{bid}_B(t{-}\ell_B),\ \mathrm{bid}_C(t{-}\ell_C)\bigr),
  \qquad
  \mathrm{ask}^{\mathrm{fair}}_t = \min\!\bigl(\mathrm{ask}_B(t{-}\ell_B),\ \mathrm{ask}_C(t{-}\ell_C)\bigr),
\]
with $\mathrm{mid}^{\mathrm{fair}}_t = \tfrac{1}{2}(\mathrm{bid}^{\mathrm{fair}}_t + \mathrm{ask}^{\mathrm{fair}}_t)$.
The choice of the cross-venue \emph{best} rather than a volume-weighted
average is a defence against being arbitraged: clients can always
transact at the tighter side elsewhere, so anything wider on $A$ is
free optionality handed to adversarial flow. HFTs read the same
feeds at $\ell_{\mathrm{HFT}} = 50\,\mathrm{ms}$, so the price we
quote against is always structurally stale relative to theirs; this
gap is priced explicitly as a spread component in
Section~\ref{sec:quoter-spread}.

\subsection{Reservation price: Avellaneda--Stoikov with infinite horizon}
\label{sec:quoter-reservation}

The classical inventory-shift mechanism of \citet{avellaneda2008high}
uses a finite horizon $T$ with the penalty $\gamma\sigma^2(T-t)$.
That formulation is inappropriate for a $24/5$ FX market: there is
no terminal liquidation time at which inventory becomes worthless.
We replace $T-t$ by a stationary discount $1/\omega$ with
$\omega = 1/(8\,\mathrm{h})$ --- one FX session as the effective risk
horizon --- which is the infinite-horizon limit of the same HJB
system, studied formally by \citet{gueant2013dealing}.

A second correction is numerical. Applying the raw Avellaneda--Stoikov
shift with inventory in EUR (range $0$--$900\mathrm{k}$) produces a
reservation displacement of several hundred basis points at ten
percent inventory, three orders of magnitude larger than the
half-spread itself. We therefore work with the normalised ratio
$\rho = q/K$ and express the shift as a fraction of the half-spread,
so that at $|\rho|=1$ the quoted centre is displaced by exactly one
half-spread:
\[
  r_t \;=\; \mathrm{mid}^{\mathrm{fair}}_t \;-\; \rho \cdot h_t.
\]
Direction is preserved (a long EUR position drags the centre down
and attracts sells); magnitude is now calibrated to the spread
itself, with no new free parameter beyond $\gamma$.

\subsection{Three-component spread with fee floor}
\label{sec:quoter-spread}

The half-spread $h_t$ is built as the sum of three economically
distinct adverse-selection premia, floored by a fee-cover term,
\[
  h_t \;=\; \tfrac{1}{2}\bigl(h^{\mathrm{AS}}_t + h^{\mathrm{lat}}_t + h^{\mathrm{inv}}_t\bigr),
  \qquad h_t \;\geq\; \phi \cdot \mathrm{fee}^A_{\mathrm{maker}} \cdot \mathrm{mid}^{\mathrm{fair}}_t.
\]
The Avellaneda--Stoikov component
\[
  h^{\mathrm{AS}}_t(\mathrm{bps}) \;=\; \gamma \cdot (\sigma\cdot 100)^2 \cdot \tfrac{1}{\omega}
  \;+\; \tfrac{2}{\gamma}\,\ln\!\bigl(1 + \gamma/k\bigr)
\]
combines inventory-risk aversion (first term) with the convexity of
the exponential order-arrival intensity (second term), as derived by
\citet{avellaneda2008high} after the infinite-horizon substitution.
The latency term
$h^{\mathrm{lat}}_t = 2\sigma_{\mathrm{sec}}\sqrt{\Delta\ell}$, with
$\Delta\ell = w_B(\ell_B-\ell_{\mathrm{HFT}}) + w_C(\ell_C-\ell_{\mathrm{HFT}})$,
is two standard deviations of the expected adverse move during the
window in which HFTs see the reference feeds and we do not --- a
cushion against the free option they hold against our stale quotes.
The capacity term $h^{\mathrm{inv}}_t = \alpha_s \rho^2 h^{\mathrm{AS}}_t$
is quadratic in the inventory ratio: it is negligible near flat and
widens sharply as we approach the delta limit, pushing flow away
from the side that would deepen our position. Finally the floor
$\phi \cdot \mathrm{fee}^A_{\mathrm{maker}} \cdot \mathrm{mid}^{\mathrm{fair}}_t$
guarantees that the inception spread covers the maker fee on every
fill: no trade is ever gross-negative, only fee-negative offset by
subsequent inventory P\&L. The floor binds in calm regimes where the
three adversarial premia would otherwise collapse below the fee.

\subsection{Asymmetric skew and ladder}
\label{sec:quoter-ladder}

The reservation shift in Section~\ref{sec:quoter-reservation} is
symmetric: it moves both sides of the quote by the same amount.
\citet{gueant2017optimal} shows that the asymptotic optimum is
instead an \emph{asymmetric} split of the half-spread --- widen the
side that would deepen inventory, tighten the side that would reduce
it. We therefore apply the Guéant skew
\[
  \Delta_t \;=\; q \cdot \sqrt{\frac{\gamma\sigma^2}{2k}},
  \qquad
  \mathrm{ask}^{\mathrm{post}}_t = r_t + h_t - \Delta_t,
  \qquad
  \mathrm{bid}^{\mathrm{post}}_t = r_t - h_t - \Delta_t,
\]
with $\Delta_t$ clipped so the tighter side can never breach the
fee floor.

The subject requires ten levels on each side. Levels step one tick
further from the mid at each rung; sizes decay exponentially and
are skewed against inventory,
\[
  \mathrm{size}^{\mathrm{bid}}_i \;=\; Q_0\,e^{-\beta i}\,(1 - \tfrac{1}{2}\overline{\rho}),
  \qquad
  \mathrm{size}^{\mathrm{ask}}_i \;=\; Q_0\,e^{-\beta i}\,(1 + \tfrac{1}{2}\overline{\rho}),
\]
with $\overline{\rho} = \mathrm{clip}(\rho,-1,1)$. This is a second,
complementary inventory correction acting through \emph{depth}
rather than \emph{price}: even if the Guéant skew is clipped by
the fee floor, the ladder sizes still bias against further
accumulation. Exponential decay concentrates displayed liquidity at
the top of book, consistent with the empirical shape of
limit-order-book queues.

\subsection{Selective re-quoting}
\label{sec:quoter-requote}

Re-quoting every step is expensive in cancel/post messages and
costly in time priority: orders that are still valid lose their
queue position on every spurious cancel. We use a strict
six-priority hierarchy, with each lower priority firing only if
none above it did (Table~\ref{tab:quoter-requote}). Priority~2
treats the $08{:}00$ and $16{:}00$ UTC FX session boundaries as
hard resets of the full ladder, so session-specific state does not
accumulate across regimes. Priority~3 closes the price-drift leak;
priority~5 closes a subtler silent-accumulation leak where market
prices are flat but our own inventory has moved enough to
invalidate the ladder skew. Priority~6 fires on pure staleness and
re-quotes at a tighter $0.7\times$ spread, so the refreshed quotes
compete back into relevance rather than being re-posted at the
same passive distance.

\begin{table}[H]
  \centering
  \footnotesize
  \begin{tabular}{cll}
    \toprule
    \textbf{P} & \textbf{Trigger} & \textbf{Action} \\
    \midrule
    1 & First call & Full ladder, no cancels \\
    2 & Session boundary ($08{:}00$/$16{:}00$ UTC) & Cancel all, full ladder \\
    3 & $|$best-price drift$|>0.25\,\mathrm{spread}$ & Cancel all, full ladder \\
    4 & Fills / top-ups pending & Rebuild filled slots only \\
    5 & $|\Delta q|/K>5\%$ since last reprice & Cancel all, full ladder \\
    6 & Order older than $\tau_{\mathrm{stale}}$ & Cancel stale, reprice at $0.7\times$ spread \\
    \bottomrule
  \end{tabular}
  \caption{Requote priorities; at most one rule fires per step.}
  \label{tab:quoter-requote}
\end{table}

\subsection{Hedge router}
\label{sec:quoter-hedge}

When either $|q| > \delta_{\mathrm{lim}}\cdot K/2$ or
$|q \cdot \mathrm{mid}^{\mathrm{fair}}| > \delta_{\mathrm{lim}}\cdot K/2$
--- that is, either the EUR leg or its USD notional breaches the
delta limit on half-capital --- we externalise risk through taker
market orders on $B$ and $C$. Three decisions shape the router.
First, the USD notional of EUR inventory is valued at the $B/C$
cross-venue mid, not at $\mathrm{mid}_A$, because $A$'s mid is
polluted by our own skewed quotes. Second, the split between
venues is depth-aware: each venue is scored by
\[
  s_v \;=\; \frac{1}{\mathrm{fee}^v_{\mathrm{taker}}
                      \;+\; \sigma_{\mathrm{sec}} \cdot \ell_v
                      \;+\; \lambda \cdot \mathrm{mid}^{\mathrm{fair}}/D_v},
\]
combining the taker fee, the expected adverse move during execution
lag, and a market-impact penalty inversely proportional to the
available depth $D_v$ at the lagged step. The hedge is split
$s_B:(s_B+s_C)$ with overflow re-routed to the other venue when the
preferred one is depth-constrained. Third, when post-hedge inventory
remains above the tighter threshold $\mathrm{hedge\_partial\_limit}\cdot K/2$
--- meaning the combined $B{+}C$ depth was insufficient to bring us
back --- we flip an emergency flag that multiplies the
Avellaneda--Stoikov inventory-risk term by $5\times$ on the next step.
Our own quotes on $A$ become so aggressively asymmetric that organic
client flow cleans up the residual. This is the
\citet{gueant2013dealing} inventory-penalty mechanism used as an
overflow valve: we deliberately do not chase depth we cannot reach.

