\documentclass[12pt,a4paper]{article}

% ── Encoding & fonts ──────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

% ── Page layout ───────────────────────────────────────────────────────────────
\usepackage[top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]{geometry}

% ── Math ──────────────────────────────────────────────────────────────────────
\usepackage{amsmath}
\usepackage{amssymb}

% ── Figures & tables ──────────────────────────────────────────────────────────
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{array}

% ── Code listings ─────────────────────────────────────────────────────────────
\usepackage{listings}
\usepackage{xcolor}

\lstset{
  basicstyle=\ttfamily\small,
  backgroundcolor=\color{gray!10},
  frame=single,
  rulecolor=\color{gray!40},
  breaklines=true,
  breakatwhitespace=true,
  showstringspaces=false,
  tabsize=2,
}

% ── References & links ────────────────────────────────────────────────────────
\usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}

% ── Misc ──────────────────────────────────────────────────────────────────────
\usepackage{nicefrac}
\usepackage{enumitem}
\usepackage{parskip}

% ── Section styling ───────────────────────────────────────────────────────────
\usepackage{titlesec}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

% ─────────────────────────────────────────────────────────────────────────────
\title{\textbf{FX Market Making --- EUR/USD Simulation\\[6pt]
       \large User Guide}}

\author{
  Edouard Blanc \quad Cl\'ement Dardare \quad Julien Simeoni \\[4pt]
  \small Paris Dauphine University --- MSc 203
}

\date{April 2026}
% ─────────────────────────────────────────────────────────────────────────────

\begin{document}

\maketitle
\tableofcontents
\newpage

% =============================================================================
\section{Project Overview}
% =============================================================================

This repository contains a full simulation of a market-maker (MM) operating on
the EUR/USD pair. The project models the complete MM lifecycle: price path
generation, order book management, client order flow, P\&L tracking, parameter
calibration, and competition against HFT agents.

\subsection*{Market architecture}

\begin{itemize}
  \item \textbf{Exchange A} --- the MM's own venue. It posts bid/ask quotes on a
        multi-level order book and earns the spread on client fills.
  \item \textbf{Market B} --- a reference market with a wide spread
        (75\% vol weight, 200\,ms refresh). Used for hedging large inventory positions.
  \item \textbf{Market C} --- a fast reference market with a tight spread
        (25\% vol weight, 170\,ms refresh). Used for urgent hedges.
  \item \textbf{Client flow} --- a Poisson-driven stream of market orders whose
        size and direction depend on the mid price, spread, and time of day.
  \item \textbf{HFT agents} (Phase 3) --- high-frequency traders competing for
        fills on exchange A, following a realistic intraday activity schedule.
\end{itemize}

\subsection*{Simulation phases}

\begin{center}
\begin{tabular}{llll}
\toprule
\textbf{Phase} & \textbf{Config} & \textbf{Stock path} & \textbf{Purpose} \\
\midrule
Phase 1            & Heuristic \texttt{QuoterConfig}    & Seed    & Baseline with default parameters \\
Calibration        & ---                                 & ---     & Fit MM parameters from Phase 1 data \\
Phase 1 Calibrated & Calibrated config                  & Same seed & Before/after comparison \\
Phase 2            & Calibrated config                  & Seed P2 & Out-of-sample test \\
Phase 3            & Calibrated config + HFT            & Seed P2 & Full competitive environment \\
\bottomrule
\end{tabular}
\end{center}

% =============================================================================
\section{Installation}
% =============================================================================

Python 3.12 is required. All dependencies are managed with \texttt{uv}.

\begin{lstlisting}[language=bash]
pip install uv          # install uv if not already present
uv sync                 # install all project dependencies
pip install PySide6     # required for the desktop app
\end{lstlisting}

% =============================================================================
\section{How to Run}
% =============================================================================

There are two ways to run the full simulation pipeline.

\subsection{Option A --- Desktop App (recommended)}

A full GUI with parameter controls, live progress bars, and interactive tabbed
result windows for each phase.

\begin{lstlisting}[language=bash]
python3.12 main.py
\end{lstlisting}

\noindent See Section~\ref{sec:app} for the complete app workflow.

\subsection{Option B --- Standalone Script}

A terminal script that runs the exact same pipeline sequentially. It pauses
between phases so you can review results before continuing. Edit the parameters
block at the top of the file before running.

\begin{lstlisting}[language=bash]
python3.12 run_simulation.py
\end{lstlisting}

\noindent See Section~\ref{sec:script} for details on configuring the script.

% =============================================================================
\section{Desktop App Workflow}
\label{sec:app}
% =============================================================================

\subsection*{Parameters}

Set all parameters before running. They are read at the moment each button is clicked.

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Field} & \textbf{Description} & \textbf{Default} \\
\midrule
Model       & Price process: \texttt{GARCH}, \texttt{GBM}, or \texttt{Heston} & GARCH \\
Seed        & Stock path seed for Phase 1 and Comparison & 32 \\
Seed P2     & Stock path seed for Phase 2 and Phase 3 & 99 \\
N Days      & Simulation duration for Phase 1 \& Comparison (days) & 30 \\
DT (s)      & Time step for Phase 1 \& Comparison (seconds) & 0.1 \\
N Days P2   & Simulation duration for Phase 2 \& 3 (days) & 15 \\
DT P2 (s)   & Time step for Phase 2 \& 3 --- finer grid for HFT & 0.05 \\
Vol         & Annualised volatility & 0.07 \\
Origin      & Starting EUR/USD price & 1.10 \\
Capital K   & Market-maker capital (EUR/USD) & 1\,000\,000 \\
Quote size  & EUR notional per side per HFT agent (Phase 3) & 2\,000 \\
\bottomrule
\end{tabular}
\end{center}

GARCH fields ($\alpha$, $\beta$, $\lambda$, $\sigma_J$) and Heston fields
($\kappa$, $\theta$, $\xi$, $\rho$) appear automatically when the corresponding
model is selected.

\subsection*{Step-by-step workflow}

Buttons are greyed out until their prerequisites are met. Follow the steps in order.

\medskip
\noindent\textbf{Step 1 --- Simulate Stock}\\
Simulates the EUR/USD price path with the chosen model and Seed.

\medskip
\noindent\textbf{Step 2 --- Build Markets}\\
Constructs Markets B and C (spread arrays, depth levels) from the simulated
stock. Required before running any phase.

\medskip
\noindent\textbf{Step 3 --- Run Phase 1}\\
Runs the market-maker with the heuristic \texttt{QuoterConfig} on the stock
path from Seed. Opens a result window with the backtesting report and all
diagnostic figures.

\medskip
\noindent\textbf{Step 4 --- Run Calibration}\\
Fits a \texttt{QuoterConfig} from Phase 1 data. Opens a Calibration Summary
window showing all calibrated parameter values. \textit{Requires Phase 1.}

\medskip
\noindent\textbf{Step 5 --- Phase 1 Calibrated --- Compare}\\
Re-runs the market-maker on the exact same stock path (Seed) with the calibrated
config. Direct before/after comparison: identical market conditions, updated
quoting parameters. \textit{Requires Calibration.}

\medskip
\noindent\textbf{Step 6 --- Run Phase 2}\\
Runs the market-maker with the calibrated config on a fresh stock path (Seed P2),
at the finer time grid (DT P2, N Days P2). Out-of-sample test.

\medskip
\noindent\textbf{Step 7 --- Run Phase 3 (HFT)}\\
Same as Phase 2 but adds HFT agents with a realistic intraday activity schedule.
HFT agents post quotes on both sides at the configured quote size.

\subsection*{Result windows}

Each phase opens an independent tabbed window:
\begin{itemize}
  \item \textbf{Report} --- full backtesting text (scrollable, monospace font).
  \item \textbf{Figure 1\ldots N} --- each figure in a scrollable canvas with the
        matplotlib toolbar (zoom, pan, save).
  \item \textbf{Last figure} --- \texttt{QuoterConfig} parameter summary.
\end{itemize}

Multiple windows can be open simultaneously and closed independently.

% =============================================================================
\section{Standalone Script Configuration}
\label{sec:script}
% =============================================================================

Edit the parameters block at the top of \texttt{run\_simulation.py}:

\begin{lstlisting}[language=Python]
MODEL     = "GARCH"   # "GARCH" | "GBM" | "Heston"
SEED      = 32        # stock seed for Phase 1 and Comparison
SEED_P2   = 99        # stock seed for Phase 2 & 3

N_DAYS    = 30        # days for Phase 1 & Calibrated Comparison
DT_SEC    = 0.1       # time step for Phase 1 & Comparison (seconds)
N_DAYS_P2 = 15        # days for Phase 2 & 3
DT_SEC_P2 = 0.05      # time step for Phase 2 & 3 (seconds)

VOL      = 0.07
ORIGIN   = 1.10
CAPITAL  = 1_000_000

# Toggle individual phases on/off
RUN_PHASE1            = True
RUN_CALIBRATION       = True
RUN_PHASE1_CALIBRATED = True
RUN_PHASE2            = True
RUN_PHASE3_HFT        = True
\end{lstlisting}

The script pauses between phases with a \textit{Continue} dialog, allowing you
to inspect each result window before proceeding. All windows stay open until you
close them at the end.

% =============================================================================
\section{Simulation Pipeline}
% =============================================================================

\subsection*{Step 1 --- Price path simulation}

A EUR/USD mid price is generated using one of three models:

\begin{itemize}
  \item \textbf{GBM} --- Geometric Brownian Motion. Log-normal diffusion with
        constant volatility.
  \item \textbf{Heston} --- Stochastic volatility. Mean-reverting variance
        process; captures vol clustering without jumps.
  \item \textbf{GARCH} --- GARCH(1,1) with optional jump component. Captures
        volatility clustering, fat tails, and sudden price shocks.
\end{itemize}

\subsection*{Step 2 --- Market B \& C construction}

Two reference markets are built from the same price path:
\begin{itemize}
  \item \textbf{Market B} --- wider spread (Skew model), deeper book
        (500\,k EUR mean depth). Used for hedging when inventory is large.
  \item \textbf{Market C} --- tighter spread (Adaptive model), shallower book
        (200\,k EUR mean depth). Used for urgent hedges.
\end{itemize}

\subsection*{Step 3 --- Phase 1 (heuristic quoting)}

The MM runs on exchange A with a default \texttt{QuoterConfig}. At each step,
\texttt{compute\_quotes()} selects which levels to reprice using a 5-priority
system. Client orders arrive via a Poisson process; fills update inventory and
schedule hedges on Markets B or C.

\subsection*{Step 4 --- Calibration}

\texttt{CalibratedConfigBuilder} fits a new \texttt{QuoterConfig} from Phase 1
data using five independent calibrators run in parallel:

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Calibrator} & \textbf{What it fits} \\
\midrule
\texttt{VolatilityCalibrator} & EWMA volatility $\to$ dynamic spread width \\
\texttt{SpreadCalibrator}     & OLS regression $\to$ target half-spread \\
\texttt{KCalibrator}          & Fill-rate intensity $k$ $\to$ Poisson arrival model \\
\texttt{StaleCalibrator}      & Stale-quote threshold $\to$ refresh frequency \\
\texttt{GammaOptimizer}       & Inventory penalty $\gamma$ $\to$ A-S optimal skew \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Step 5 --- Phase 1 Calibrated (comparison)}

The MM runs on the same stock path with the calibrated config. Comparing Phase 1
and Phase 1 Calibrated on identical conditions isolates the direct impact of
calibration.

\subsection*{Step 6 --- Phase 2 (out-of-sample)}

The calibrated config is tested on a fresh stock path (Seed P2) at a finer time
grid ($\Delta t = 0.05\,\text{s}$, 15 days). This is the true out-of-sample
evaluation.

\subsection*{Step 7 --- Phase 3 (HFT competition)}

HFT agents are added to exchange A. They follow a realistic intraday schedule
and operate in four states:

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{State} & \textbf{Behaviour} \\
\midrule
\texttt{ACTIVE}        & Posting competitive quotes on both sides \\
\texttt{ONE\_SIDED\_BID} & Quoting bids only (inventory squeeze) \\
\texttt{ONE\_SIDED\_ASK} & Quoting asks only (inventory squeeze) \\
\texttt{OFFLINE}       & Not quoting (vol spike or connectivity loss) \\
\bottomrule
\end{tabular}
\end{center}

% =============================================================================
\section{Parameters Reference}
% =============================================================================

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Parameter} & \textbf{Description} & \textbf{Default} \\
\midrule
\texttt{MODEL}       & Price process                                   & \texttt{GARCH} \\
\texttt{SEED}        & Stock path seed for Phase 1 and Comparison      & 32 \\
\texttt{SEED\_P2}    & Stock path seed for Phase 2 and Phase 3         & 99 \\
\texttt{N\_DAYS}     & Trading days for Phase 1 \& Comparison          & 30 \\
\texttt{DT\_SEC}     & Time step for Phase 1 \& Comparison (s)         & 0.1 \\
\texttt{N\_DAYS\_P2} & Trading days for Phase 2 \& 3                   & 15 \\
\texttt{DT\_SEC\_P2} & Time step for Phase 2 \& 3 (s)                  & 0.05 \\
\texttt{VOL}         & Annualised volatility                            & 0.07 \\
\texttt{ORIGIN}      & Starting EUR/USD price                           & 1.10 \\
\texttt{CAPITAL}     & Market-maker capital K (EUR/USD)                 & 1\,000\,000 \\
\texttt{HFT\_QUOTE\_SIZE\_EUR} & EUR notional per HFT side (Phase 3)  & 2\,000 \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{GARCH parameters (active when \texttt{MODEL = "GARCH"})}

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Parameter} & \textbf{Description} & \textbf{Default} \\
\midrule
\texttt{GARCH\_ALPHA}   & ARCH coefficient $\alpha$                         & 0.05 \\
\texttt{GARCH\_BETA}    & GARCH coefficient $\beta$ (requires $\alpha+\beta<1$) & 0.94 \\
\texttt{GARCH\_LAM}     & Jump intensity (jumps/year, 0 = no jumps)         & 100 \\
\texttt{GARCH\_SIGMA\_J}& Jump size standard deviation (log-return)         & 0.005 \\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Heston parameters (active when \texttt{MODEL = "Heston"})}

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Parameter} & \textbf{Description} & \textbf{Default} \\
\midrule
\texttt{HESTON\_KAPPA} & Mean-reversion speed of variance          & 2.0 \\
\texttt{HESTON\_THETA} & Long-run variance (set to $\sigma^2$)     & 0.0049 \\
\texttt{HESTON\_XI}    & Volatility of volatility                  & 0.3 \\
\texttt{HESTON\_RHO}   & Price / variance correlation              & $-0.1$ \\
\bottomrule
\end{tabular}
\end{center}

\end{document}
